%\providecommand{\main}{..}  % *Modification: redefine path location, must go before \documentclass
\documentclass[../minutes.tex]{subfiles}
\begin{document}
%\begin{multicols*}{2}

\chapter{A Silly Example}
\section{Old Business}
Last year we had a meeting about the meeting.  We decided to have a meeting about the meeting.  We had a meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We decided to have a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting.  We had a meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting about the meeting

\section{Progress}
This year we made lots of progress.

\section{Agreements}
We agreed to make more progress.

\section{Next Steps}
Begin work on progress.

\bib{}
%\end{multicols*}
\end{document}

